---
title: "Introduction to Rcppzhuoer"
author: "Zhuoer Dong"
date: "`r Sys.Date()`"
output: 
    prettydoc::html_pretty
        toc: yes
vignette: >
  %\VignetteIndexEntry{Introduction to Rcppzhuoer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# convert list to tibble

`as_tibble()` converts a _non-empty_ `List` of _equal-length_ elements into a tibble.

```{Rcpp}
# include <Rcpp.h>
// [[Rcpp::depends(Rcppzhuoer)]]
# include <Rcppzhuoer.h>
using namespace Rcpp;

//[[Rcpp::export]]
List demo_as_tibble() {
    // construct a list
    IntegerVector a = IntegerVector::create(1, 2, 3);
    CharacterVector b = CharacterVector::create("a", "b", "c");
    List l = List::create(Named("a") = a, Named("b") = b);
    
    return Rcppzhuoer::as_tibble(l);
}
```

```{r}
demo_as_tibble()
```

# paste arguments into a std::string

`paste()` can recieve arbitrary number and types of arguments.

It converts them into strings via `<<` operator, then concatenate into a single `std::string`. 

Besides, We enable `std::boolalpha`. 


```{Rcpp}
# include <Rcpp.h>
// [[Rcpp::depends(Rcppzhuoer)]]
# include <Rcppzhuoer.h>
using namespace Rcpp;

//[[Rcpp::export]]
void demo_paste() {
    std::string str = Rcppzhuoer::paste("hello ", 'h', "adle", 'y', " * ", 3.5);
    Rcout << str << std::endl; 
    
    Rcout << Rcppzhuoer::paste("a true: ", 1, ' ', true);
}
```


```{r}
demo_paste()
```
